\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
added an additional sentence relating back to related work in conclusion/futurework
chore(paper): cleaned up a couple of typos

Similar to ByteBuddy, there doesn't seem to be any work on recommendations of what classes to modify. Both tools require a decent amount of knowledge of the target source code. ByteBoy could eventually, using its HPROF and {\tt javap} anaylsis, support ByteBuddy and AspectJ synthesis as well. However, code synthesis for both of these tools would prove to be a different challenge on its own.

@@

Future work may be conducted on the instrumentation phase of our approach, as it would be interesting to consider the results of performing different dynamic analysis algorithms on the target program in an attempt to generate a more comprehensive set of Byteman rules. Additionally, more work will be done to improve the grammar file of the language extension, and it will hopefully be available for download via the Visual Studio Marketplace in the near future.

>>>>

Similar to ByteBuddy, there doesn't seem to be any work on recommendations of what classes to modify. Both tools require a decent amount of knowledge of the target source code. Byteboy could eventually, using its HPROF and {\tt javap} analysis, support ByteBuddy and AspectJ synthesis as well. However, code synthesis for both of these tools would prove to be a different challenge on its own.

@@

Future work may be conducted on the instrumentation phase of our approach, as it would be interesting to consider the results of performing different dynamic analysis algorithms on the target program in an attempt to generate a more comprehensive set of Byteman rules. Additionally, more work will be done to improve the grammar file of the language extension, and it will hopefully be available for download via the Visual Studio Marketplace in the near future. Support for other existing Java tools, such as AspectJ and ByteBuddy, could be useful as developers would not need to learn an additional language (Byteman).
